Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-12-11 paper/paper.tex
Simulation of 3team in URTS, done. - Make URTS 3 team figure.
Revise paper, Section II and III.

Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability. Additionally, the complementarity between them also makes such a system more potential \cite{arbanas2018decentralized}. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing. To discuss more concretely, we consider a hybrid UAVs-UGVs team system for S\&R. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the S\&R environment, we choose biped robot as UGV. Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.

@@

\section{PRELIMINARIES OF URTS in S\&R usage}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a goal (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of goal. 
% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location assigned by task allocation algorithm and then make a decision to avoid obstacles and other agents nearby.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to determine specific behavior to follow the path found by path planning algorithm according to the situation of the environment especially for agents with complex mechanical systems like robots. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in URTS are not always following the path. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral layer is necessary.
% The behavior layer decides an appropriate behavior based on the circumstances.

In order to make a behavior, we must design a corresponding motion by local motion planning. The motion is a prescribed reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed for each agent to follow this desired reference trajectory.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map, start point and object information. The 5 blocks on right hand side are the flow of an agent performing a S\&R mission. From the top to the bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destination $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Path Planning}
After a destination $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithms to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete the pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner. Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the URTS.

\begin{remark}
    To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}. However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate. Therefore, when the paths collide, the mechanism of waiting for the other side to pass can be used to avoid the collision problem.
\end{remark}

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robots). In this case, an unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning. The path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints. The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by the previous block, task allocation block. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumptions are made.

@@

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be due to a goal changing that is made by human or task allocation block. For robot, it can be a collision detected by a dynamic roadmap-based planner. The resulting path $(\sigma_n)$ is passed to the next block, Behavior Layer.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$. The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. (a) The local motion planning of each agent in URTS . The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block. For UAVs, the moving block is predefined in (b). For robots, the moving block is predefined in (c). (b) The moving block of each UAV where the flying block is predefined in \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in \ref{fig:FandW}}
    \label{fig:LMP}
\end{figure*}

In Fig. \ref{fig:LMP}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to the moving behavior in Fig. \ref{fig:LMP}. A more detailed description will be given in the next section.

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed.
    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

>>>>

Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability. Additionally, the complementarity between them also makes such a system more potential \cite{arbanas2018decentralized}. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAVs-UGVs team system will be more appealing. To discuss more concretely, we consider a hybrid UAVs-UGVs team system for S\&R. For the need for search mobility, we choose quadrotor aircraft as UAV. In order to deal with the complex terrain of the S\&R environment, we choose biped robot (referred to as "robot" in this article) as UGV. Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.

@@

\section{PRELIMINARIES OF URTS in S\&R usage}
The URTS will start with a given S\&R area, and end with the S\&R mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. 
% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location determined by the task and then make a decision to avoid obstacles and other agents nearby through a path planning algorithm.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in URTS are not always following the path. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral layer is necessary.
% The behavior layer decides an appropriate behavior based on the circumstances.

In order to make a behavior, we must design a corresponding motion by local motion planning. The motion is a prescribed reference path for an actual mechanical system to follow. Finally, a tracking controller is designed for each agent to follow this desired reference path.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information. The 5 blocks on right hand side are the flow of an agent performing a S\&R mission. From the top to the bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Path Planning}
After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithms to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete the pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner. Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the proposed URTS architecture.

\begin{remark}
    To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}. However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate. Therefore, an alternative solution is to use single-agent path planning together with the mechanism of waiting for the other agent to pass first in the event of a collision.
\end{remark}

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for biped robot). In this case, an unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning. The path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints. The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or "waypoints"), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or "map") $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by the previous block, task allocation block. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumptions are made.

@@

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be due to a goal changing that is made by human or task allocation block. For robot, it can be a collision detected by a dynamic roadmap-based planner. The resulting path $(\sigma_n)$ is passed to the next block, behavior layer block.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$ (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it). The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. (a) The local motion planning of each agent in URTS . The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or discrete signal) designed by a specific behavior block. For UAVs, the moving block is predefined in (b). For robots, the moving block is predefined in (c). (b) The moving block of each UAV where the flying block is predefined in Fig. \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in Fig. \ref{fig:FandW}}
    \label{fig:LMP}
\end{figure*}

In Fig. \ref{fig:LMP}, some basic behaviors of UAV and robot mentioned in Fig. \ref{fig:behavior} are given to futher illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to the moving behavior in Fig. \ref{fig:LMP}. A more detailed description will be given in the next section.

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed.
    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore the nonholonomic constraints (the velocity and acceleration constraints).
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable holonomic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure this error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

\subsection{motion planning of flying of UAV}
A dynamic model about how an UAV in URTS moves in the physical world is given first. By Newton-Euler equation, the dynamic model of each UAV in URTS can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f_u \\ \tau_u
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % Form 2 of rotation matrix R(\Theta)
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f_u =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau_u=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame as shown in Fig. 2.8 in \cite{sabatino2015quadrotor}, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame. This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$. For UAV, the reference trajectory $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$ is in the task space, where the subscript $r$ denotes the reference.

\textit{
    \begin{remark}
        Since the UAV (quadrotor) has four rotors, we only have four control input. To simplify the model, the UAV dynamic model in (\ref{eq:uav}) considers the actuator control input $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors. Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system. This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be inversely calculated through other degrees of freedom that can be assigned arbitrarily and the dynamic equation in (\ref{eq:uav}).
    \end{remark}
}

Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \psi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.
